Attack-Tolerance in Structured Networks via Multipath Routing \\ Draft: 2016-02-18

### 2016-02-19 ec-2016/source/paper.tex
Add date.
paper

% Title portion
\title{
Attack-Tolerance in Structured Networks via Multipath Routing
\\ Draft: 2016-02-16
}
\author{EDWARD L. PLATT
\affil{University of Michigan}
DANIEL M. ROMERO
\affil{University of Michigan}}

@@

In this paper, we formally evaluate the effects of network structure on
attack-resistance. We also propose an efficient, fault-tolerant network architecture.
Our analysis focuses on {\em structured networks},
in which links between nodes are constrained to a particular architecture.
The proposed fault-tolerant architecture utilizes {\em multipath routing},
in which many possible paths exist betweeen two nodes on a communication network.
In our case, multiple paths allow multiple copies of a message to be sent,
which can be used for error-detection and error-correction by the receiver.

@@

We now construct a path such that between trusted neighborhoods $z^{(t)}$ is always
in $S_s$, $R_s$, or both, guaranteeing that the path does not overlap with the
other paths $v_r^{(t)}$.
Routing proceeds in stages, with the level $l$ increasing by 1 at each hop.
In Stage 1 ($0 \leq t < h$), down or down-right edges
are chosen such that the the $t$th bit of $z^{(t+1)}$ is equal to the $t$th bit
of $s$. Throughout Stage 1, all nodes are within the sender's trusted neighborhood.
At the end of Stage 1, $z^{(h)} \in S_s$, and $z^{(t)}$ will remain so until the level loops
back to $0$ at $t = m$.

>>>>

% Title portion
\title{
Attack-Tolerance in Structured Networks via Multipath Routing
\\ Draft: 2016-02-18
}
\author{EDWARD L. PLATT
\affil{University of Michigan}
DANIEL M. ROMERO
\affil{University of Michigan}}

@@

We consider a setting in which a source node in a network attempts to route information
to a target node by forwarding it through the edges of the network. We 
assume that some nodes in the network may be compromised by an attacker 
and will forward the wrong information to their neighbors. We assume 
a weak form of trust transitivity, where the source and the target are able to 
detect any compromised nodes that are a few hops away from them in the network.

Given this framework, we develop a \emph{multipath routing} technique to reduce 
the likelihood that compromised nodes are undetected during the information 
routing process by allowing multiple copies of a message to be sent through independent paths,
which can be used for error-detection and error-correction by the receiver.

The multipath routing technique relies on the existence and detectability of
multiple independent paths between the source and the destination. Thus, network 
structure and routing algorithms play a key role in the success of the technique. We formally evaluate the 
effects of network structure on attack-resistance and show that the probability of undetected 
errors decreases exponentially with the number of independent paths between 
source and destination. Focusing on {\em structured networks}, in which links between nodes are 
constrained to a particular architecture, we propose an efficient multipath routing algorithm on an popular network
architecture, which is currently used for several applications -- the butterfly network \cite{}.

@@

We now construct a path such that between trusted neighborhoods $z^{(t)}$ is always
in $S_s$, $R_s$, or both, guaranteeing that the path does not overlap with the
other paths $v_r^{(t)}$.
Routing proceeds in stages, with the level $l$ increasing by 1 at each hop.
In Stage 1 ($0 \leq t < h$), down or down-right edges
are chosen such that the $t$th bit of $z^{(t+1)}$ is equal to the $t$th bit
of $s$. Throughout Stage 1, all nodes are within the sender's trusted neighborhood.
At the end of Stage 1, $z^{(h)} \in S_s$, and $z^{(t)}$ will remain so until the level loops
back to $0$ at $t = m$.
